Patchwork: Incremental Computation for Abstract Interpretation

### 2019-02-19 paper.tex
Restructure w/explicit contributions + thread

@@

Parity analysis (requires lattice)\\
Interval analysis (requires widening)\\
Octagon analysis (relational)

\section{Datalog Strategy - Limitations + Comparison}

@@

\begin{enumerate}
    \item Define a set of relations.\\
    For this problem, there are 6 relations total - 4 "input relations", which are the base facts, and 2 "derived relations", which give the information we're interested in. They are as follows: New(v, h), Assign(v, v), Store(v, f, v), Load(v, v, f) are the inputs, and VarPointsTo(v, h) and HeapPointsTo(h, f, h) are the derived relations. Here the lowercase letters are types - v for variable, h for heap, f for field.
    \newpage

@@

@@

\section{Contribution: Extending to Incremental Analysis Framework}

We use the discussed data structures in a modular framework for implementing static analyses. Our framework requires the implementation of an abstract domain, including transfer function, to be given by the user. This approach allows us to take advantage of existing libraries used in the static analysis community. For this paper, we interfaced with APRON, an existing library supporting the numerical domains necessary for interval and octagon analysis. Once we have defined the language to operate on - in our case, Jimple - and the transfer function for our domain of choice (see examples), we can incrementally execute the analysis.

See figures 1/2 for an outline of the driving functions for the incremental analysis. By exploiting the structure of the typical 'worklist' algorithm for static analysis, we can achieve incremental performance gains.

Our naming strategy works by reference to (insert defense of naming strategy - strictly location?) (reference to analysis trace visualization - given by Benno in table 3)

We evaluated our approach on a spread of analyses and target programs.

Analyses:\\
Interval, octagon.

Programs:\\
IncA benchmarks?

Edit model:\\
Adopt IncA approach?

We compare to: IncA, off-the-shelf analysis?

We show: same alarm rates as off-the-shelf analysis, similar incremental performance as IncA. QoIs: cumulative time, alarm rates, false alarm rates

We need: off-the-shelf analysis to use, benchmarks to use, edit model to use

Interprocedural? Or doing that now?

%% Appendix
\appendix
\section{Appendix}

Text of appendix \ldots

>>>>

We make the following contributions:

\begin{enumerate}
    \item We propose an efficient incremental naming strategy for the worklist algorithm over a CFG.
    \item We provide an incremental abstract interpretation framework which can express any domain of interest. (Wording? Any domain + widening operator? Point is frees the monotonicity restriction)
    \item We demonstrate that our framework is competitive, performance-wise, with 'Datalog-style' alternatives.
\end{enumerate}

@@

Parity analysis (C1: demonstrates naming strategy)\\
Interval analysis (C2: demonstrates extra expressivity)\\
(C3 handled empirically in evaluation section)

\section{Contribution: Naming Strategy for Worklist Algorithms}

We present our naming strategy for the generic worklist algorithm. You are convinced that this naming strategy gives some efficiency guarantee for an arbitrary analysis using this algorithm.\\

We contextualize our strategy via our simplest motivating example (parity).

\section{Contribution: Expressive Abstract Interpretation Framework}

We use the discussed algorithm in a modular framework for implementing abstract interpretation over arbitrary domains. Our framework requires the implementation of an abstract domain, including transfer function, to be given by the user. This approach allows us to take advantage of existing libraries used in the static analysis community. For this paper, we interfaced with APRON, an existing library supporting the numerical domains necessary for interval and octagon analysis. Once we have defined the language to operate on - in our case, Jimple - and the transfer function for our domain of choice (see examples), we can incrementally execute the analysis.

Our evaluation seeks to answer several core research questions:

\begin{enumerate}
    \item Does Patchwork achieve significant performance gains on incremental edits relative to a non-incremental baseline tool? (check overhead/speedup constants)
    \item Is Patchwork competitive with alternative tools for incremental static analysis (IncA)? (direct comparison on parity analysis)
    \item Is the added expressivity of Patchwork relevant to clients? (check false alarm rates on impoverished interval analysis v. regular)
\end{enumerate}

We evaluated Patchwork on a series of benchmark programs (IncA's) using parity analysis, bad interval analysis, and normal interval analysis. We compare Patchwork's speed to Jandom on parity analysis (just that?). We compare Patchwork's speed to IncA on bad interval analysis. We compare the false alarm rate of the normal interval analysis to that of the bad interval analysis.

Interprocedural? Or doing that now?\\
Improving naming strategy? Or specializing it to different domains?\\
Incremental relation data structure?

%% Appendix
\appendix
\section{Appendix: Datalog Strategy - Limitations + Comparison}

@@

\begin{enumerate}
    \item Define a set of relations.\\
    For this problem, there are 6 relations total - 4 "input relations", which are the base facts, and 2 "derived relations", which give the information we're interested in. They are as follows: New(v, h), Assign(v, v), Store(v, f, v), Load(v, v, f) are the inputs, and VarPointsTo(v, h) and HeapPointsTo(h, f, h) are the derived relations. Here the lowercase letters are types - v for variable, h for heap, f for field.

@@

Choosing the Datalog strategy does not allow the user to directly reference the program of interest in their analysis. Instead, they must 'compile' the program into a new set of facts/relations relevant to their analysis. Often, as in IncA's interval analysis, a considerable amount of scaffolding relations are necessary to retain awareness of the program's control flow, and the user must correctly connect the program's semantics to the relations and types written for Datalog, which requires consideration of two distinct domains. In contrast, the Adapton approach allows us to directly write abstract transfer functions over the concrete semantics of our language of choice, removing a layer of abstraction.\\

@@
